Towards a standardized evaluation of imputation methodology

### 2022-03-31 Formatted/Formatted.tex
Before cleaning up comments in the manuscript

\begin{document}
%\DOIsuffix{bimj.DOIsuffix}
\DOIsuffix{bimj.200100000}
\Volume{52}
\Issue{61}
\Year{2010}
\pagespan{1}{}
\keywords{Evaluation; Imputation; Missing data; Simulation studies;\\ [1pc]
% \noindent \hspace*{-4.2pc} Supporting Information for this article is available from Github, \break \hspace*{-4pc} \underline{github.com/gerkovink/StandardizedEvaluation}.
% } %%% semicolon and fullpoint added here for keyword style
\noindent \hspace*{-4pc} Supporting Information for this article is available online from \\
\hspace*{-4pc} \underline{gerkovink.com/evaluation}. 
}  %%% semicolon and fullpoint added here for keyword style

@@

\begin{table}[h]
\caption{Checklist for reporting on imputation methodology evaluations}
\begin{tabular}{ll}
% \hline
%   & Suggested aspects to report                                                       \\
\hline
1 & Simulation scope                                                                   \\ \cline{2-2}
  & Aim                                                                                \\
  & Design (incl. pseudo-code or flow diagram)                                         \\
  & Number of simulation repetitions                                                   \\ \hline
2 & Comparative truth                                                                  \\ \cline{2-2}
  & Data-generating mechanism (model-based or design-based)                            \\
  & Sampling variance                                                                  \\
%  & Data characteristics (number of observations, number of variables, variable types, \\
%  & coherence between variables incl. data structures e.g. clustering)                 \\
  & Data characteristics (incl. multivariate relations and structures e.g. clustering) \\
  & Estimand                                                                           \\ \hline 
3 & Induced missingness                                                                \\ \cline{2-2}
  & Missingness mechanism (incl. type or functional form of the missing data   model)  \\
  & Missingness pattern (incl. missingness proportion)                                 \\ \hline 
4 & Applied methods                                                                    \\ \cline{2-2}
  & Imputation methods (incl. parameters e.g. the number of imputations)               \\
  & Analytic methods (incl. calculation of standard errors e.g. pooling   rules)       \\
  & Reference method (e.g. complete case analysis)                                    \\ \hline 
5 & Imputation evaluation                                                              \\ \cline{2-2}
  & Imputation-generating process (e.g. algorithmic non-convergence)                   \\
  & Imputation model fit (e.g. posterior predictive checks)                            \\
  & Distributional characteristics (e.g. plausibility of imputed values)               \\ \hline 
6 & Performance evaluation                                                             \\ \cline{2-2}
  & Statistical properties (e.g. confidence validity)                                  \\
  & Comparative performance (e.g. predictive accuracy)                                 \\ \hline
\end{tabular}
\end{table}

>>>>

\begin{document}
%\DOIsuffix{bimj.DOIsuffix}
\DOIsuffix{bimj.200100000}
\Volume{52}
\Issue{61}
\Year{2010}
\pagespan{1}{}
\keywords{Evaluation; Imputation; Missing data; Simulation studies;\\ [1pc]
% \noindent \hspace*{-4.2pc} Supporting Information for this article is available from Github, \break \hspace*{-4pc} \underline{github.com/gerkovink/StandardizedEvaluation}.
% } %%% semicolon and fullpoint added here for keyword style
\noindent \hspace*{-4pc} Supporting Information for this article is available from \underline{gerkovink.com/evaluation}.\\
% \hspace*{-4pc} \underline{gerkovink.com/evaluation}. 
}  %%% semicolon and fullpoint added here for keyword style

@@

Table \ref{table:check} provides a checklist for reporting on imputation methodology evaluations.

\begin{table}[ht]
\caption{Checklist for reporting on imputation methodology evaluations}
\label{table:check}
\begin{tabular}{ll}
% \hline
%   & Suggested aspects to report                                                       \\
\hline
1 & Simulation scope                                                                   \\ \cline{2-2}
  & Aim                                                                                \\
  & Design (incl. pseudo-code or flow diagram)                                         \\
  & Number of simulation repetitions                                                   \\ \hline
2 & Comparative truth                                                                  \\ \cline{2-2}
  & Data-generating mechanism (model-based or design-based)                            \\
  & Sampling variance                                                                  \\
%  & Data characteristics (number of observations, number of variables, variable types, \\
%  & coherence between variables incl. data structures e.g. clustering)                 \\
  & Data characteristics (incl. multivariate relations and structures e.g. clustering) \\
  & Estimand                                                                           \\ \hline 
3 & Induced missingness                                                                \\ \cline{2-2}
  & Missingness mechanism (incl. type or functional form of the missing data   model)  \\
  & Missingness pattern (incl. missingness proportion)                                 \\ \hline 
4 & Applied methods                                                                    \\ \cline{2-2}
  & Imputation methods (incl. parameters e.g. the number of imputations)               \\
  & Analytic methods (incl. calculation of standard errors e.g. pooling   rules)       \\
  & Reference method (e.g. complete case analysis)                                    \\ \hline 
5 & Imputation evaluation                                                              \\ \cline{2-2}
  & Imputation-generating process (e.g. algorithmic non-convergence)                   \\
  & Imputation model fit (e.g. posterior predictive checks)                            \\
  & Distributional characteristics (e.g. plausibility of imputed values)               \\ \hline 
6 & Performance evaluation                                                             \\ \cline{2-2}
  & Statistical properties (e.g. confidence validity)                                  \\
  & Comparative performance (e.g. predictive accuracy)                                 \\ \hline
\end{tabular}
\end{table}
